A general and efficient representation of ancestral recombination graphs

### 2024-06-03 paper.tex

Aside from these practical challenges, there is also a deeper
issue with the implicit strategy of basing an ARG data structure on
recording events and their properties (e.g.\ the crossover breakpoint
for a recombination event). This approach 
% assumes all events are \emph{knowable}, and does not
necessitates that all events are recorded explicitly, and does not 
provide an obvious mechanism for either aggregating multiple events
or expressing uncertainty about them. While this is not a
problem when describing the results of simulations, for instance (where all details
are perfectly known), it is an issue when we wish to
formally describe the output of inference methods which do not
necessarily attempt to infer events that are not \emph{knowable} from the data, particularly
as datasets approach the population scale~\citep[e.g.][]{
turnbull2018hundred, bycroft2018genome,hayes20191000,
Ros-Freixedes2020,karczewski2020mutational,tanjo2021practical,
halldorsson2022sequences}.

>>>>

Aside from these practical challenges, there is also a deeper
issue with the implicit strategy of basing an ARG data structure on
recording events and their properties (e.g.\ the crossover breakpoint
for a recombination event). This approach 
requires all events to be recorded explicitly, and does not 
provide an obvious mechanism for either aggregating multiple events
or expressing uncertainty about them. This is not a
problem when describing the results of simulations, where all details
are perfectly known. However, it can be an issue when we wish to
formally describe the output of various inference methods, particularly
those that avoid inferring events that are not \emph{knowable} from the data:
a useful approach as datasets approach the population scale~\citep[e.g.][]{
turnbull2018hundred, bycroft2018genome,hayes20191000,
Ros-Freixedes2020,karczewski2020mutational,tanjo2021practical,
halldorsson2022sequences}).
